Check Coverage

### 2019-08-06 analysis/merge_data.Rmd
Add joggle argument to qhull calculation to fix precision problems.

get_fd <- function(data){
  species_mat <- data %>%
    select(year, id) %>% 
    arrange(year, id) %>%
    mutate(present = 1) %>%
    spread(id, value = present, fill = 0) %>%
    select(-year)

@@

  as.tibble(dbFD(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .)
}

@@

test_data <- biotime_traits %>% 
  filter(study_id %in% c(39, 46, 47, 51)) %>%
  group_by(study_id) %>%
  nest() %>%
  mutate(metrics = map(data, ~get_fd_safe(.x))) %>%
  filter(!is.na(metrics)) %>%
  select(-data) %>%
  unnest()
```

>>>>

get_fd <- function(data){
  #print(max(data$record_id))
  species_mat <- data %>%
    select(year, id) %>% 
    arrange(year, id) %>%
    mutate(present = 1) %>%
    spread(id, value = present, fill = 0) %>%
    select(-year)

@@

  as.tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .)
}

@@

test_data <- biotime_traits %>% 
  group_by(study_id, plot) %>%
  nest() %>%
  mutate(metrics = map(data, ~get_fd_safe(.x))) %>%
  filter(!is.na(metrics)) %>%
  select(-data) %>%
  unnest()
```
